Standartox: A tool to derive exposure endpoints from chemical test results

### 2019-10-29 article/parts/04_technical_validation.tex
Updates from Overleaf

>>>>

We sampled an entry for each of the 50 most occurring concentration units and compared the Standartox conversions to manually calculated conversions for these, to guarantee the correctness of unit conversions. The same was done for six samples of duration units (See \ref{tab:chck-unit}

To guarantee correctness of unit conversions we sampled an entry for each of the 50 most frequent concentration units. and the six most frequent duration units, respectively.

Out of the 1229 concentration units in the EPA ECOTOX data base, Standartox retains only those (n = X) whih are convertible to one of the following units: ug/l, ul/l, ppb, g/m2, mg/kg, \%, resulting in 873473 out of 952625 test results. Likewise, out of the 125 test duration units in the EPA ECOTOX, Standartox retains only those (n = X) which are accurately convertible to hours, leading to 905110 out of 952625 test results (see table \ref{tab:units-duration}). % TODO

The here described Standartox version uses the EPA ECOTOX data base released on the 12.09.2019.

### 2019-10-29 article/parts/05_usage_notes.tex
Updates from Overleaf

\subsubsection*{Standartox Filters}

@@

Users can define several input parameters \ref{tab:inputs} in the application's graphical user interface (GUI), handled in the ui.R script in order to adjust the aggregation according specific requirements. In doing so users execute R functions (fun\_filter.R, fun\_aggregation.R, fun\_filagg\_plot\_ly.R) loaded in the server.R script, which produce a 'filtered' and an 'aggregated' data set as well as an interactive overview plot. Only the 'aggregated' data set is presented in the GUI. However, both data sets can be downloaded via a download button.

@@

The R-package standartox

@@

>>>>

@@

In Standartox web application (app) users can define several input parameters \ref{tab:inputs} through the app's graphical user interface (GUI) in order to filter the data specifically and perform the aggregation. The aggregated result is then shown as a table as well as an overview plot and can then be downloaded as a 'filtered' and an 'aggregated' data set \ref{fig:standartox_app}.

\begin{figure}
    \includegraphics[width=1\linewidth]{article/figures/screenshot_standartox_app.png}
    \caption{Standartox web application}
    \label{fig:standartox_app}
\end{figure}

@@

The R-package standartox consists of the two functions stx\_catalog() and stx\_query(). The former allows the retrieval of a catalog of possible parameters that can be used as an input for the latter. stx\_query() fetches the toxicity values from the data base. It returns a R list object following the app containing a 'filtered' and 'aggregated' R data.frame object. Additionally ...................

@@

The units are denoted as ppm or ppb which comprises ug/l and mg/l

List the units which are kept.

Thereby 'food', soil, ai and other information are lost but these are coded in other variables anyway. And they don't belong in a unit variable. Characteristic for ecotoxicology

units such as per day (mg/kg/day) are generally excluded.
